Make any stupid plot you want

### 2020-12-21 draft/sections/math.tex
rearranging/changing/cleaning up diagrams

\begin{equation}
    A: \tau \rightarrow \rho
\end{equation}

@@

\begin{equation}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[r, "\pi" description] & B  \\
    \end{tikzcd}
\end{equation}

@@

\begin{equation}
    \begin{tikzcd}
        \pi^{-1}(U) \arrow[r, "\varphi" description] \arrow[d, "\pi" description] & U \times F \arrow[ld, "\mathrm{proj}_U"] \\
        U                                                                         &                                         
    \end{tikzcd}
    \label{eq:local_trivial}
\end{equation}
such that $\varphi: \pi^{-1}(U) \rightarrow U \times F$ is a homeomorphism where $\pi$ and $\mathrm{proj}_U$ both map to $U$ and the fiber over $k$ $F_b = \pi^{-1}({b \in B}) $ is homomorphic to the fiber $F$.

The section $f$ is the mapping from base space to total space $f: B\rightarrow E$ 
\begin{equation}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi" description]    \\
                          & B \arrow[u, "f" description, bend right]
        \end{tikzcd}
\end{equation}

@@

\subsubsection{Sheaf and Stalk}
As described in equation~\ref{eq:local_trivial}, there is a local space $U \subset B$ around every $b$. The inclusion map $\iota: U \rightarrow B$ can be pulled back such that $\iota^{*}E$ is the space of $E$ restricted over $U$. 
\begin{equation}
    \begin{tikzcd}
        \iota^*E \arrow[d, "\pi"']           & E \arrow[d, "\pi"'] \arrow[l, "\iota^*" description]                    \\
        U \arrow[u, "\iota^*f"', bend right] & B \arrow[u, "f" description, bend right] \arrow[l, "\iota" description]
        \end{tikzcd}
\end{equation}

The localized section of fibers $\iota^*\f: U \rightarrow \iota^*E$ is the sheaf $O(E)$ with germ of $\xi^*f$. The neighborhood of points the sheaf lies over is the stalk $\mathscr{F}_b$ \cite{StalkSheaf2019,spanier1989algebraic}

@@

\subsubsection{Base Space $K$}

@@

\begin{equation}
    \begin{tikzcd}
            U_{\sigma} \arrow[d, "\pi_{\sigma}" description] \arrow[r] & U \arrow[d, "\pi" description] \\
            C \arrow[r, "\sigma" description]                          & DT                            
    \end{tikzcd}
\end{equation}
The pullback $U_{\sigma} \coloneqq \sigma^{-1}(U)$ restricts $U$ to the datatypes of the fields in $C$ such that $U_{\sigma}$ is the fiber product $U \times_{DT} C$, and the pullback $\pi_{\sigma}:U_{\sigma} \rightarrow C$ specifies the domain bundle $U_{\sigma}$ over $C$ induced by $\sigma$. The fiber $F$ is the cartesian product of all sets in the disjoint union $U_{\sigma}$.

@@

Every point $k \in K$ maps to a space $S_{k} \in S$, which is the topology of the output of the artist $A$. The space $H$ is a total space representing the predisplay space, with a fiber dependent on the render space and a base space of $\S$:
\begin{equation}
    \begin{tikzcd}
        D \arrow[r, hook] & H \arrow[d, "\pi" description, bend right] \\
                                    & S \arrow[u, "\rho" description, bend right] 
    \end{tikzcd}
\end{equation}

where $\rho: S \rightarrow H$ is mapping from a region $s$ on a mathematical encoding of the image to a region $xy$ on the screen that the renderer then maps to pixel space. For a physical screen display, the predisplay space is a trivial fiber bundle $H=\mathbb{R}^{7}\times S$ such that $\rho$ is
\begin{equation}
    \rho(s)  = \{x, y, z, g, b, a\}
    \label{eq:rho}
\end{equation}

To draw an image, a region, $H$ is inverse mapped into a region $s \in S$ where
\begin{equation}
s = \rho^{-1}_{XY}(xy)
\end{equation}
such that the rest of the fields in $\mathbb{R}^{7}$ are then integrated over $s$ to yield the remaining fields in $p$
%%change the integral to a double integral
\begin{align}
    R(p) &= \iint_s \rho_R(s)ds^{2}\\
    G(p) &= \iint_s \rho_G(s)ds^{2}\\
    B(p) &= \iint_s \rho_B(s)ds^{2}
\end{align}

@@

The first stage of the artist $F: E \rightarrow V$ maps from data space to visual variable  \cite{carpendaleVisualRepresentationSemiology,bertinIIPropertiesGraphic2011,munznerWhatDataAbstraction2014} space
%%include the $
\begin{equation}
    \begin{tikzcd}
        E \arrow[r, "\nu" description]                                & V \\
        K \arrow[u, "\tau" description] \arrow[ru, "\mu" description] &  
    \end{tikzcd}
\end{equation}

such that $\nu: \tau \mapsto \mu$ is a homorphism where $\tau$ and $\mu$ are equivariant such that the properties of the field type persist in the visual representation. The map $\xi: S \rightarrow K$ goes from a region $s$ to it associated $k$ %%remove the taus from the diagram
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi" description]              & H \arrow[d, "\pi" description]                                    \\
        K \arrow[u, "\tau" description, bend right] & S \arrow[l, "\xi" description] \arrow[lu, "\xi^*\tau" description]
        \end{tikzcd}
\end{equation}
such that when $\xi(s) = k$, there is a mapping from screen space to k  $\xi^*\tau(s) = \tau(k)$. The visual fiber bundle $V$ gets pulled back over $S$ via $\xi$ such that 
\begin{equation}
    \begin{tikzcd}
        \xi^*V \arrow[r, "q"']                      & H \\
        S \arrow[u, "\xi^*\mu"] \arrow[ru, "\rho"'] &  
        \end{tikzcd}
\end{equation}
the composition $q \circ \xi^*\mu$ generates the $\rho$ function described in section~\ref{sec:display}.

>>>>

@@

\begin{equation}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[r, "\pi"] & B
    \end{tikzcd}
\end{equation}

@@

\begin{equation}
    \begin{tikzcd}
        \pi^{-1}(U) \arrow[r, "\varphi"] \arrow[d, "\pi"'] & U \times F \arrow[ld, "\mathrm{proj}_U"] \\
        U                                                  &                                         
    \end{tikzcd}
    \label{eq:local_trivial}
\end{equation}
such that $\varphi: \pi^{-1}(U) \rightarrow U \times F$ is a homeomorphism where $\pi$ and $\mathrm{proj}_U$ both map to $U$ and the fiber over $k$ $F_b = \pi^{-1}({b \in B}) $ is homomorphic to the fiber $F$.

The section $f$ is the mapping from base space to total space $f: B\rightarrow E$ 
\begin{equation}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi"']           \\
        & B \arrow[u, "f"', bend right]
    \end{tikzcd}
\end{equation}

@@

\subsubsection{Sheaf and Stalk}
As described in equation~\ref{eq:local_trivial}, there is a local space $U \subset B$ around every $b$. The inclusion map $\iota: U \rightarrow B$ can be pulled back such that $\iota^{*}E$ is the space of $E$ restricted over $U$. 
\begin{equation}
    \begin{tikzcd}
        \iota^*E \arrow[d, "\pi"']           & E \arrow[d, "\pi"'] \arrow[l, "\iota^*"']         \\
        U \arrow[u, "\iota^*f"', bend right] & B \arrow[u, "f"', bend right] \arrow[l, "\iota"']
        \end{tikzcd}
\end{equation}

The localized section of fibers $\iota^*f: U \rightarrow \iota^*E$ is the sheaf $O(E)$ with germ of $\xi^*f$. The neighborhood of points the sheaf lies over is the stalk $\mathscr{F}_b$ \cite{StalkSheaf2019,spanier1989algebraic}

@@

\subsubsection{Base Space}

@@

\begin{equation}
    \begin{tikzcd}
        U_{\sigma} \arrow[d, "\pi_{\sigma}"'] \arrow[r] & U \arrow[d, "\pi"] \\
        C \arrow[r, "\sigma"]                           & DT                
    \end{tikzcd}
\end{equation}
The pullback $U_{\sigma} \coloneqq \sigma^{-1}(U)$ restricts $U$ to the datatypes of the fields in $C$ such that $U_{\sigma}$ is the fiber product $U \times_{DT} C$, and the pullback $\pi_{\sigma}:U_{\sigma} \rightarrow C$ specifies the domain bundle $U_{\sigma}$ over $C$ induced by $\sigma$. The fiber $F$ is the cartesian product of all sets in the disjoint union $U_{\sigma}$.

@@

Every point $k \in K$ maps to a space $S_{k} \in S$, which is the topology of the output of the artist $A$. The space $H$ is a total space representing the predisplay space, with a fiber dependent on the render space and a base space of $S$:
\begin{equation}
    \begin{tikzcd}
        D \arrow[r, hook] & H \arrow[r, "\pi"] &S\\   
        \end{tikzcd}
\end{equation}

Where the section $\rho: S \rightarrow H$
\begin{equation}
    \begin{tikzcd}
        D \arrow[r, hook] & H \arrow[d, "\pi"']              \\
                          & S \arrow[u, "\rho"', bend right]
        \end{tikzcd}
\end{equation}

 is mapping from a region $s$ on a mathematical encoding of the image to a region $xy$ on the screen that the renderer then maps to pixel space. For a physical screen display, the predisplay space is a trivial fiber bundle $H=\mathbb{R}^{7}\times S$ such that $\rho$ is
\begin{equation}
    \rho(s)  = \{x, y, z, r, g, b, a\}
    \label{eq:rho}
\end{equation}

To draw an image, a region, $H$ is inverse mapped into a region $s \in S$ where
\begin{equation}
s = \rho^{-1}_{\tiny{XY}}(xy)
\end{equation}
such that the rest of the fields in $\mathbb{R}^{7}$ are then integrated over $s$ to yield the remaining fields:
%%change the integral to a double integral
\begin{align}
    r &= \iint\limits_s \rho_{\tiny{R}}(s)ds^{2}\\
    g &= \iint\limits_s \rho_{\tiny{G}}(s)ds^{2}\\
    b &= \iint\limits_s \rho_{\tiny{B}}(s)ds^{2}
\end{align}

@@

The first stage of the artist $F: E \rightarrow V$ maps from data space to visual variable  \cite{carpendaleVisualRepresentationSemiology,bertinIIPropertiesGraphic2011,munznerWhatDataAbstraction2014} space
%%include the $
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi"'] \arrow[r, "\nu"]                                        & V \arrow[ld, "\pi"'] \\
        K \arrow[u, "\tau"', bend right] \arrow[ru, "\mu"', bend right, shift left] &                     
        \end{tikzcd}
\end{equation}

such that $\nu: \tau \mapsto \mu$ is a homorphism where $\tau$ and $\mu$ are equivariant such that the properties of the field type persist in the visual representation. The map $\xi: S \rightarrow K$ goes from a region $s$ to it associated $k$
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi"'] & H \arrow[d, "\pi"'] \\
        K                   & S \arrow[l, "\xi"']
        \end{tikzcd}
\end{equation}
such that when $\xi(s) = k$, there is a mapping from screen space to k  $\xi^*\tau(s) = \tau(k)$. The visual fiber bundle $V$ gets pulled back over $S$ via $\xi$ such that 
\begin{equation}
    \begin{tikzcd}
        \xi^*V \arrow[r, "q"']                      & H \\
        S \arrow[u, "\xi^*\mu"] \arrow[ru, "\rho"'] &  
        \end{tikzcd}
\end{equation}
the composition $q \circ \xi^*\mu$ generates the $\rho$ function described in section~\ref{sec:display}.
